Characterization and evolution of hourly extreme precipitation in France using an Explicit-Convection Regional Climate Model

### 2025-11-10 article/fig6.qmd
figs independant

---
title: ""
format:
  pdf:
    listings: false
    documentclass: standalone
    classoption: ["border=4pt"]
    keep-tex: true
execute:
  echo: false
  warning: false
  message: false
header-includes:
  - \usepackage{graphicx}
  - \usepackage{tabularx}
  - \usepackage{array}
  - \usepackage{makecell}
  - \usepackage{multirow}
  - \usepackage{caption}
  - \input{macros_fig5.tex}
---

@@

trend_pluie_hydro = assemble(
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/hydro/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/hydro/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/legend_signif.svg",
  "figures/trend_pluie_hydro.svg"
)
trend_pluie_ond = assemble(
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/ond/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/ond/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/legend_signif.svg",
  "figures/trend_pluie_ond.svg"
)
trend_pluie_jfm = assemble(
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/jfm/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/jfm/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/legend_signif.svg",
  "figures/trend_pluie_jfm.svg"
)
trend_pluie_amj = assemble(
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/amj/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/amj/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/legend_signif.svg",
  "figures/trend_pluie_amj.svg"
)
trend_pluie_jas = assemble(
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/jas/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/jas/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/legend_signif.svg",
  "figures/trend_pluie_jas.svg"
)
df_trend_pluie_hydro = combined_all.loc[(combined_all["echelle"] == "quotidien") & (combined_all["season"] == "hydro") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_pluie_ond = combined_all.loc[(combined_all["echelle"] == "quotidien") & (combined_all["season"] == "ond") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_pluie_jfm = combined_all.loc[(combined_all["echelle"] == "quotidien") & (combined_all["season"] == "jfm") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_pluie_amj = combined_all.loc[(combined_all["echelle"] == "quotidien") & (combined_all["season"] == "amj") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_pluie_jas = combined_all.loc[(combined_all["echelle"] == "quotidien") & (combined_all["season"] == "jas") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
```

```{python}
#| include: false
def _first_vals(df):
    # .item() évite les objets numpy scalaires
    r = float(df["r"].iloc[0].item())
    n = int(df["n"].iloc[0].item())
    me = float(df["me"].iloc[0].item())
    return r, n, me

r_ond, n_ond, me_ond = _first_vals(df_trend_pluie_ond)
r_jfm, n_jfm, me_jfm = _first_vals(df_trend_pluie_jfm)
r_amj, n_amj, me_amj = _first_vals(df_trend_pluie_amj)
r_jas, n_jas, me_jas = _first_vals(df_trend_pluie_jas)
r_hyd, n_hyd, me_hyd = _first_vals(df_trend_pluie_hydro)

@@

\newcommand{{\rHYDRO}}{{{r_hyd:.2f}}}
\newcommand{{\nHYDRO}}{{{n_hyd:d}}}
\newcommand{{\meHYDRO}}{{{me_hyd:+.2f}}}
"""
with open("macros_fig5.tex", "w", encoding="utf-8") as f:
    f.write(macros)
```

```{=latex}
\begingroup
% ---- Grille principale en pleine largeur ----
\noindent
\begin{minipage}[t]{\paperwidth}
\centering
\setlength{\tabcolsep}{0pt}
\renewcommand{\arraystretch}{1}
\begin{tabularx}{\paperwidth}{
  >{\centering\arraybackslash}m{0.49\paperwidth}
  >{\centering\arraybackslash}m{0.49\paperwidth}
}

% --- Ligne 1 ---
\textbf{\small OND} & \textbf{\small JFM} \\[-0.5mm]
\small $r=\ \rOND$ \ (n=\ \nOND) & \small $r=\ \rJFM$ \ (n=\ \nJFM) \\[-0.5mm]
\small $ME=\ \meOND\%$ & \small $ME=\ \meJFM\%$ \\[-0.5mm]
\includegraphics[width=\linewidth]{figures/trend_pluie_ond.pdf} &
\includegraphics[width=\linewidth]{figures/trend_pluie_jfm.pdf} \\

% --- Ligne 2 ---
\textbf{\small AMJ} & \textbf{\small JAS} \\[-0.5mm]
\small $r=\ \rAMJ$ \ (n=\ \nAMJ) & \small $r=\ \rJAS$ \ (n=\ \nJAS) \\[-0.5mm]
\small $ME=\ \meAMJ\%$ & \small $ME=\ \meJAS\%$ \\[-0.5mm]
\includegraphics[width=\linewidth]{figures/trend_pluie_amj.pdf} &
\includegraphics[width=\linewidth]{figures/trend_pluie_jas.pdf} \\

% --- Ligne 3 ---
\textbf{\small HYDRO} &
\multirow{3}{*}{
  \begin{minipage}[c]{\linewidth}
    \centering
    \includegraphics[width=0.85\linewidth,keepaspectratio]{../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/legend_horiz_signif.pdf}
    \makebox[0.85\linewidth][c]{\small \%}
  \end{minipage}
}\\[-0.5mm]

@@

\includegraphics[width=\linewidth]{figures/trend_pluie_hydro.pdf} &
\begin{minipage}[c]{\linewidth}
  \centering
  \vspace{0.5em}
  \begin{minipage}[c]{0.90\linewidth}
    \setlength{\parindent}{0pt}
    \small
    \setcounter{figure}{4}% prochaine légende = Figure 5
    \captionof{figure}{
      \vspace{0.3em}
      Seasonal analysis of relative trends from 1995 to 2022 (\%) in the 10-year return level
      between the AROME model (left) and Météo-France stations (right), with the correlation ($r$),
      the number of stations compared (n), and the bias ($ME$) derived from daily precipitation maxima
      from 1959 to 2022.
      \vspace{0.3em}
    }
  \end{minipage}
\end{minipage}
\\

>>>>

---
title: ""
format:
  pdf:
    listings: false
    documentclass: standalone
    classoption: ["border=4pt"]
    keep-tex: true
execute:
  echo: false
  warning: false
  message: false
header-includes:
  - \usepackage{graphicx}
  - \usepackage{tabularx}
  - \usepackage{array}
  - \usepackage{makecell}
  - \usepackage{multirow}
  - \usepackage{caption}
  - \input{macros_fig6.tex}
---

@@

trend_horaire_pluie_hydro = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/hydro/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/hydro/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_hydro.svg"
)
trend_horaire_pluie_ond = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/ond/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/ond/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_ond.svg"
)
trend_horaire_pluie_jfm = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/jfm/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/jfm/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_jfm.svg"
)
trend_horaire_pluie_amj = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/amj/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/amj/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_amj.svg"
)
trend_horaire_pluie_jas = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/jas/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/jas/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_jas.svg"
)
df_trend_horaire_pluie_hydro = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "hydro") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_horaire_pluie_ond = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "ond") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_horaire_pluie_jfm = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "jfm") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_horaire_pluie_amj = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "amj") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_horaire_pluie_jas = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "jas") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
```

```{python}
#| include: false
def _first_vals(df):
    r = float(df["r"].iloc[0].item())
    n = int(df["n"].iloc[0].item())
    me = float(df["me"].iloc[0].item())
    return r, n, me

r_ond, n_ond, me_ond = _first_vals(df_trend_horaire_pluie_ond)
r_jfm, n_jfm, me_jfm = _first_vals(df_trend_horaire_pluie_jfm)
r_amj, n_amj, me_amj = _first_vals(df_trend_horaire_pluie_amj)
r_jas, n_jas, me_jas = _first_vals(df_trend_horaire_pluie_jas)
r_hyd, n_hyd, me_hyd = _first_vals(df_trend_horaire_pluie_hydro)

@@

\newcommand{{\rHYDRO}}{{{r_hyd:.2f}}}
\newcommand{{\nHYDRO}}{{{n_hyd:d}}}
\newcommand{{\meHYDRO}}{{{me_hyd:+.2f}}}
"""
with open("macros_fig6.tex", "w", encoding="utf-8") as f:
    f.write(macros)
```

```{=latex}
\begingroup
\noindent
\begin{minipage}[t]{\paperwidth}
  \centering
  \setlength{\tabcolsep}{0pt}
  \renewcommand{\arraystretch}{1}

  \begin{tabularx}{\paperwidth}{
    >{\centering\arraybackslash}m{0.49\paperwidth}
    >{\centering\arraybackslash}m{0.49\paperwidth}
  }

    % --- Ligne 1 ---
    \textbf{\small OND} & \textbf{\small JFM} \\[-0.5mm]
    \small $r=\ \rOND$ \ (n=\ \nOND) & \small $r=\ \rJFM$ \ (n=\ \nJFM) \\[-0.5mm]
    \small $ME=\ \meOND\%$ & \small $ME=\ \meJFM\%$ \\[-0.5mm]
    \includegraphics[width=\linewidth]{figures/trend_horaire_pluie_ond.pdf} &
    \includegraphics[width=\linewidth]{figures/trend_horaire_pluie_jfm.pdf} \\

    % --- Ligne 2 ---
    \textbf{\small AMJ} & \textbf{\small JAS} \\[-0.5mm]
    \small $r=\ \rAMJ$ \ (n=\ \nAMJ) & \small $r=\ \rJAS$ \ (n=\ \nJAS) \\[-0.5mm]
    \small $ME=\ \meAMJ\%$ & \small $ME=\ \meJAS\%$ \\[-0.5mm]
    \includegraphics[width=\linewidth]{figures/trend_horaire_pluie_amj.pdf} &
    \includegraphics[width=\linewidth]{figures/trend_horaire_pluie_jas.pdf} \\

    % --- Ligne 3 ---
    \textbf{\small HYDRO} &
    \multirow{3}{*}{
      \begin{minipage}[c]{\linewidth}
        \centering
        \includegraphics[width=0.85\linewidth,keepaspectratio]{../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/legend_horiz_signif.pdf}
        \makebox[0.85\linewidth][c]{\small \%}
      \end{minipage}
    }\\[-0.5mm]

@@

    \includegraphics[width=\linewidth]{figures/trend_horaire_pluie_hydro.pdf} &
    \begin{minipage}[c]{\linewidth}
      \centering
      \vspace{0.5em}
      \begin{minipage}[c]{0.90\linewidth}
        \setlength{\parindent}{0pt}
        \small
        \setcounter{figure}{5}% prochaine légende = Figure 6
        \captionof{figure}{
          \vspace{0.3em}
          Seasonal analysis of relative trends from 1995 to 2022 (\%) in the 10-year return level
          between the AROME model (left) and Météo-France stations (right), with the correlation ($r$),
          the number of stations compared (n), and the bias ($ME$) derived from \textbf{hourly} precipitation maxima
          from 1990 to 2022.
          \vspace{0.3em}
        }
      \end{minipage}
    \end{minipage}
    \\

### 2025-11-10 article/fig7.qmd
figs independant

---
title: ""
format:
  pdf:
    listings: false
    documentclass: standalone
    classoption: ["border=4pt"]
    keep-tex: true
execute:
  echo: false
  warning: false
  message: false
header-includes:
  - \usepackage{graphicx}
  - \usepackage{tabularx}
  - \usepackage{array}
  - \usepackage{makecell}
  - \usepackage{multirow}
  - \usepackage{caption}
  - \input{macros_fig6.tex}
---

@@

trend_horaire_pluie_hydro = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/hydro/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/hydro/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_hydro.svg"
)
trend_horaire_pluie_ond = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/ond/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/ond/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_ond.svg"
)
trend_horaire_pluie_jfm = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/jfm/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/jfm/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_jfm.svg"
)
trend_horaire_pluie_amj = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/amj/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/amj/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_amj.svg"
)
trend_horaire_pluie_jas = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/jas/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/jas/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_jas.svg"
)
df_trend_horaire_pluie_hydro = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "hydro") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_horaire_pluie_ond = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "ond") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_horaire_pluie_jfm = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "jfm") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_horaire_pluie_amj = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "amj") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_horaire_pluie_jas = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "jas") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
```

```{python}
#| include: false
def _first_vals(df):
    r = float(df["r"].iloc[0].item())
    n = int(df["n"].iloc[0].item())
    me = float(df["me"].iloc[0].item())
    return r, n, me

r_ond, n_ond, me_ond = _first_vals(df_trend_horaire_pluie_ond)
r_jfm, n_jfm, me_jfm = _first_vals(df_trend_horaire_pluie_jfm)
r_amj, n_amj, me_amj = _first_vals(df_trend_horaire_pluie_amj)
r_jas, n_jas, me_jas = _first_vals(df_trend_horaire_pluie_jas)
r_hyd, n_hyd, me_hyd = _first_vals(df_trend_horaire_pluie_hydro)

macros = rf"""
\newcommand{{\rOND}}{{{r_ond:.2f}}}
\newcommand{{\nOND}}{{{n_ond:d}}}
\newcommand{{\meOND}}{{{me_ond:+.2f}}}

\newcommand{{\rJFM}}{{{r_jfm:.2f}}}
\newcommand{{\nJFM}}{{{n_jfm:d}}}
\newcommand{{\meJFM}}{{{me_jfm:+.2f}}}

\newcommand{{\rAMJ}}{{{r_amj:.2f}}}
\newcommand{{\nAMJ}}{{{n_amj:d}}}
\newcommand{{\meAMJ}}{{{me_amj:+.2f}}}

\newcommand{{\rJAS}}{{{r_jas:.2f}}}
\newcommand{{\nJAS}}{{{n_jas:d}}}
\newcommand{{\meJAS}}{{{me_jas:+.2f}}}

\newcommand{{\rHYDRO}}{{{r_hyd:.2f}}}
\newcommand{{\nHYDRO}}{{{n_hyd:d}}}
\newcommand{{\meHYDRO}}{{{me_hyd:+.2f}}}
"""
with open("macros_fig6.tex", "w", encoding="utf-8") as f:
    f.write(macros)
```

@@

    % --- Ligne 1 ---
    \textbf{\small OND} & \textbf{\small JFM} \\[-0.5mm]
    \small $r=\ \rOND$ \ (n=\ \nOND) & \small $r=\ \rJFM$ \ (n=\ \nJFM) \\[-0.5mm]
    \small $ME=\ \meOND\%$ & \small $ME=\ \meJFM\%$ \\[-0.5mm]
    \includegraphics[width=\linewidth]{figures/trend_horaire_pluie_ond.pdf} &
    \includegraphics[width=\linewidth]{figures/trend_horaire_pluie_jfm.pdf} \\

    % --- Ligne 2 ---
    \textbf{\small AMJ} & \textbf{\small JAS} \\[-0.5mm]
    \small $r=\ \rAMJ$ \ (n=\ \nAMJ) & \small $r=\ \rJAS$ \ (n=\ \nJAS) \\[-0.5mm]
    \small $ME=\ \meAMJ\%$ & \small $ME=\ \meJAS\%$ \\[-0.5mm]
    \includegraphics[width=\linewidth]{figures/trend_horaire_pluie_amj.pdf} &
    \includegraphics[width=\linewidth]{figures/trend_horaire_pluie_jas.pdf} \\

    % --- Ligne 3 ---
    \textbf{\small HYDRO} &
    \multirow{3}{*}{
      \begin{minipage}[c]{\linewidth}
        \centering
        \includegraphics[width=0.85\linewidth,keepaspectratio]{../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/legend_horiz_signif.pdf}
        \makebox[0.85\linewidth][c]{\small \%}
      \end{minipage}
    }\\[-0.5mm]

    \small $r=\ \rHYDRO$ \ (n=\ \nHYDRO) & \\[-0.5mm]
    \small $ME=\ \meHYDRO\%$ & \\[-0.5mm]

    \includegraphics[width=\linewidth]{figures/trend_horaire_pluie_hydro.pdf} &
    \begin{minipage}[c]{\linewidth}
      \centering
      \vspace{0.5em}
      \begin{minipage}[c]{0.90\linewidth}
        \setlength{\parindent}{0pt}
        \small
        \setcounter{figure}{5}% prochaine légende = Figure 6
        \captionof{figure}{
          \vspace{0.3em}
          Seasonal analysis of relative trends from 1995 to 2022 (\%) in the 10-year return level
          between the AROME model (left) and Météo-France stations (right), with the correlation ($r$),
          the number of stations compared (n), and the bias ($ME$) derived from \textbf{hourly} precipitation maxima
          from 1990 to 2022.
          \vspace{0.3em}
        }
      \end{minipage}
    \end{minipage}
    \\

  \end{tabularx}
\end{minipage}
\endgroup
```

>>>>

---
title: ""
format:
  pdf:
    listings: false
    documentclass: standalone
    classoption: ["border=4pt"]
    keep-tex: true
execute:
  echo: false
  warning: false
  message: false
header-includes:
  - \usepackage{graphicx}
  - \usepackage{tabularx}
  - \usepackage{array}
  - \usepackage{makecell}
  - \usepackage{multirow}
  - \usepackage{caption}
  - \input{macros_fig7.tex}
---

@@

trend_pluie_fev = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/fev/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/fev/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_fev.svg"
)
trend_pluie_mar = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/mar/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/mar/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_mar.svg"
)
trend_pluie_jui = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/jui/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/jui/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_jui.svg"
)
trend_pluie_nov = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/nov/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/nov/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_nov.svg"
)
df_trend_pluie_fev = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "fev") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_pluie_mar = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "mar") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_pluie_jui = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "jui") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_pluie_nov = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "nov") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
```

```{python}
#| include: false
def _first_vals(df):
    if df.empty:
        raise ValueError("DataFrame vide pour ce filtre.")
    r = float(df["r"].iloc[0].item())
    n = int(df["n"].iloc[0].item())
    me = float(df["me"].iloc[0].item())
    return r, n, me

# Récupération des valeurs mois par mois (échelle horaire)
r_fev, n_fev, me_fev = _first_vals(df_trend_pluie_fev)
r_mar, n_mar, me_mar = _first_vals(df_trend_pluie_mar)
r_jun, n_jun, me_jun = _first_vals(df_trend_pluie_jui)   # jui -> JUN
r_nov, n_nov, me_nov = _first_vals(df_trend_pluie_nov)

# Génération des macros LaTeX
macros = rf"""
\newcommand{{\rFEB}}{{{r_fev:.2f}}}
\newcommand{{\nFEB}}{{{n_fev:d}}}
\newcommand{{\meFEB}}{{{me_fev:+.2f}}}

\newcommand{{\rMAR}}{{{r_mar:.2f}}}
\newcommand{{\nMAR}}{{{n_mar:d}}}
\newcommand{{\meMAR}}{{{me_mar:+.2f}}}

\newcommand{{\rJUN}}{{{r_jun:.2f}}}
\newcommand{{\nJUN}}{{{n_jun:d}}}
\newcommand{{\meJUN}}{{{me_jun:+.2f}}}

\newcommand{{\rNOV}}{{{r_nov:.2f}}}
\newcommand{{\nNOV}}{{{n_nov:d}}}
\newcommand{{\meNOV}}{{{me_nov:+.2f}}}
"""
with open("macros_fig7.tex", "w", encoding="utf-8") as f:
    f.write(macros)
```

@@

    % --- Ligne 1 ---
    \textbf{\small FEB} & \textbf{\small MAR} \\[-0.5mm]
    \small $r=\ \rFEB$ \ (n=\ \nFEB) & \small $r=\ \rMAR$ \ (n=\ \nMAR) \\[-0.5mm]
    \small $ME=\ \meFEB\%$ & \small $ME=\ \meMAR\%$ \\[-0.5mm]
    \includegraphics[width=\linewidth]{figures/trend_horaire_pluie_fev.pdf} &
    \includegraphics[width=\linewidth]{figures/trend_horaire_pluie_mar.pdf} \\

    % --- Ligne 2 ---
    \textbf{\small JUN} & \textbf{\small NOV} \\[-0.5mm]
    \small $r=\ \rJUN$ \ (n=\ \nJUN) & \small $r=\ \rNOV$ \ (n=\ \nNOV) \\[-0.5mm]
    \small $ME=\ \meJUN\%$ & \small $ME=\ \meNOV\%$ \\[-0.5mm]
    \includegraphics[width=\linewidth]{figures/trend_horaire_pluie_jui.pdf} &
    \includegraphics[width=\linewidth]{figures/trend_horaire_pluie_nov.pdf} \\

    % --- Ligne 3 ---
    \mbox{} &
    \begin{minipage}[c]{\linewidth}
      \centering
      \includegraphics[width=0.85\linewidth,keepaspectratio]{../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/legend_horiz_signif.pdf}
      \makebox[0.85\linewidth][c]{\small \%}
    \end{minipage}
    \\

  \end{tabularx}

  \vspace{0.75em}
\end{minipage}
\endgroup
```
